PANCHANGE_data_merging

### 2020-12-04 PANCHANGE_data_merging.Rmd
small tweak during review. New knit

# Import data
```{r export data}
glad <- read_rds(file = paste0(data_path, "/glad.rds"))
dim(glad)

edgi <- read_rds(file = paste0(data_path, "/edgi.rds"))
dim(edgi)

nbr <- read_rds(file = paste0(data_path, "/nbr.rds"))
dim(nbr)

ramp <- read_rds(file = paste0(data_path, "/ramp.rds"))
dim(ramp)
```

>>>>

# Import data
```{r export data}
glad <- read_rds(paste0(data_path, "glad.rds"))
dim(glad)

edgi <- read_rds(paste0(data_path, "edgi.rds"))
dim(edgi)

nbr <- read_rds(paste0(data_path, "nbr.rds"))
dim(nbr)

ramp <- read_rds(paste0(data_path, "ramp.rds"))
dim(ramp)
```
